Figures to insert in text

### 2018-03-14 Chapters/Chapter02.tex
SDM minor changes in chapter numbering and in reinforcement learning.
sdm.. details

Sparse Distributed Memory (SDM) \citep{Kanerva1988} is a mathematical model of long-term memory that has a number of neuroscientific and psychologically plausible dynamics. This model may be applied in all sort of applications because of its incredible ability to closely reflect the human capacity to remember past experiences from clues of the present. For instance, when one is walking on a dark alley and is afraid of something, one cannot explain where one's fear come from. One just feels it. We may interpret this situation as clues of the present --- a dark alley; a giant metropolitan area; people going on about their lives mostly indifferent from each other; constrained routes ahead and behind you; etc. --- recalling past experiences from memory and thus generating the feeling. Our memory is able to make a parallel between previous experiences and the clues. Although one has never been in the exactly same situation, one's brain involuntarily makes an analogy and recognizes the possibility of danger. This flexibility into mapping one situation in another is an important human feature which is hard to replicate in computers.

SDM has been applied in many different fields, like pattern recognition \citep{norman2003modeling, rao1995natural}, noise reduction \citep{Meng2009}, handwriting recognition \citep{fan1997genetic}, robot automation \citep{Rajesh1998, mendes2008robot}, and so forth. \citet{Linhares2011} has showed that SDM respects the limits of short-term memory discussed by \citet{Miller1995} and \citet{Cowan2011}. Despite all those applications, there is not a reference implementation which would allow one to replicate the results published in a paper, to check the source code for details, and to improve it. Thus, even though intriguing results have been achieved using SDM, it requires great effort from researchers to build on top of previous work.

It is our belief that such a tool could bring orders of magnitude more researchers and attention if they were able to use the model, at zero cost, with an easy to use high-level language such as python, in an intuitive platform such as juypyter notebooks. Neuroscientists interested in long-term memory storage should not have to worry about high-bandwidth vector parallel computation.  This new tool provides a ready to use system in which experiments can be executed almost as soon as they are designed and it may accelerate research \citep{shen2014interactive}.

@@

\chapter{Results (vii): Information-theoretical write operation}

>>>>

Sparse Distributed Memory (SDM) \citep{Kanerva1988} is a mathematical model of long-term memory that has a number of neuroscientific and psychologically plausible dynamics. This model may be applied in all sort of applications because of its incredible ability to closely reflect the human capacity to remember past experiences from clues of the present. For instance, when one is walking on a dark alley and is afraid of something, one cannot explain where one's fear come from. One just feels it. We may interpret this situation as clues of the present --- a dark alley; a giant metropolitan area; people going on about their lives mostly indifferent from each other; constrained routes ahead and behind you; a general lack of activity; that very feeling that something isn't right... without knowing what isn't right, or even what `right' means... etc. --- recalling past experiences from memory and thus generating the feeling. Our memory is able to make a parallel between previous experiences and the clues. Although one has never been in the exactly same situation, one's brain involuntarily makes an analogy and recognizes the possibility of danger. This flexibility into mapping one situation in another is an important human feature which is hard to replicate in computers.

SDM has been applied in many different fields, like pattern recognition \citep{norman2003modeling, rao1995natural}, noise reduction \citep{Meng2009}, handwriting recognition \citep{fan1997genetic}, robot automation \citep{Rajesh1998, mendes2008robot}, and so forth. \citet{Linhares2011} has showed that SDM respects the limits of short-term memory discussed by \citet{Miller1995} and \citet{Cowan2011}. Despite all those applications, there is not a reference implementation which would allow one to replicate the results published in a paper, to check the source code for details, and to improve it. Thus, even though intriguing results have been achieved using SDM, it requires counter-productive, duplicate, effort from researchers to build on top of previous work.

It is our belief that a tool such as a framework could bring orders of magnitude more researchers and attention if they were able to use the model, at zero cost, with an easy to use high-level language such as python, in an intuitive platform such as juypyter notebooks. Neuroscientists interested in long-term memory storage should not have to worry about high-bandwidth vector parallel computation.  This new tool would provide a ready to use system in which experiments could be executed almost as soon as designed --- and it might accelerate research \citep{shen2014interactive}.

@@

\chapter{Results (ix): Information-theoretical write operation}
